cooking

### 2019-10-02 inst/cook.Rmd
permutation test

>>>>

## Suspect observation

Suppose that we subsequently observe order statistic `5,4,3,2,1`, that
is, person 5 is the best, 4 is the second best, and so on to 1 being
the worst.  Is this observation consistent with the previous dataset?

It is possible to perform a permutation test on this as follows.
First, calculate the probability of each of the $5!=120$ possible
observations (up to a constant):

```{r}
library(partitions)
imH <- indep(maxp(H))
f <- function(o){loglik(order_likelihood(o),imH,log=FALSE)}
LL <- apply(perms(5),2,f)
```

Then calculate the pvalue as the probability of obtaining the
observation or an observation more extreme:

```{r}
obs <- c(5,4,3,2,1)
(pval <- sum(LL[LL <= f(obs)])/sum(LL))
```
